Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-08-05 methodology.tex
tweak figures size
add copyright footnote; change shorthand for configurations e.g.CM -->cont-min
minor tweak for final version

The parameters for building the dragonfly network studied in our work are chosen based on the model proposed by Kim et al.~\cite{kim-micro}. 
In our dragonfly network, each group consists of $a = 8$ routers connected via all-to-all local channels. For each router, there are $p = 4$ compute nodes attached to it via terminal links. Each router also has $h = 4$ global channels used for intergroup connections. The radix of each router is hence $k = a+h+p-1 = 15$. 
The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. 
%\NOTE{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters? done! } 
The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes}.  
%\NOTE{What are these bandwidths? done!}. 
In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.

@@

\begin{table}[ht]
\begin{center}
\caption{Nomenclature for different placement and routing configurations} 
\label{tab: placement routing configs}
\begin{tabular}{l c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{3}{c}{Routing Policies} \\ 
\cmidrule(l){2-4}
Placement Policies & Minimal & Adaptive & Progressive Adaptive\\ % Column names row
\midrule % In-table horizontal line
Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
\midrule
Random  &   RM  &   RA   &  RPA   \\ 
\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}

>>>>

The parameters for building the dragonfly network studied in our work are chosen based on the model proposed by Kim et al.~\cite{kim-micro}. 
In our dragonfly network, each group consists of $a = 8$ routers connected via all-to-all local channels. For each router, there are $p = 4$ compute nodes attached to it via terminal links. Each router also has $h = 4$ global channels used for intergroup connections. The radix of each router is hence $k = a+h+p-1 = 15$. 
The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. 
%The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes}.  
%\NOTE{What are these bandwidths? done!}. 
The dragonfly link bandwidths are asymmetric, 2Gib/s for the local and terminal router-ports and 4GiB/s for the global ports, indicated by the Cray Cascade system~\cite{faanes}.
In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.

@@

\begin{table}[ht]
\begin{center}
\caption{Nomenclature for different placement and routing configurations} 
\label{tab: placement routing configs}
\begin{tabular}{l c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{3}{c}{Routing Policies} \\ 
\cmidrule(l){2-4}
Placement Policies & Minimal & Adaptive & Progressive Adaptive\\ % Column names row
\midrule % In-table horizontal line
%Contiguous  &  CM   &   CA   &  CPA   \\ % Content row 1
Contiguous  &  cont-min   &  cont-adp    &  cont-padp   \\ % Content row 1
\midrule
%Random  &   RM  &   RA   &  RPA   \\ 
Random  &   rand-min  &   rand-adp   &  rand-padp   \\ 
\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}

### 2016-08-05 study_workload_2.tex
minor tweak for final version

    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/gc-btime}
        \caption{Global Channel Saturation Time}
        \label{fig:synwkld-global-channel-stime}
    \end{subfigure}\hfill
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/lc-btime}
        \caption{Local Channel Saturation Time}
        \label{fig:synwkld-local-channel-stime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/tl-btime}
        \caption{Terminal Link Saturation Time}
        \label{fig:synwkld-terminal-link-stime}
    \end{subfigure}%
   \caption{Aggregate traffic and saturation time for Workload~\Rmnum{2} under the configurations listed in Table~\ref{tab: placement routing configs}.}
   \label{fig:synwkld-network-traffic-stime}
\end{figure*}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MultiGrid Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CrystalRouter Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MultiGrid Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CrystalRouter Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}
    \caption{Aggregate workload traffic for routers serving specific applications. More routers are involved in serving each application when random placement is in use, compared to contiguous placement.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}

>>>>

    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/gc-btime}
        \caption{Global Channel Saturation Time}
        \label{fig:synwkld-global-channel-stime}
    \end{subfigure}\hfill
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/lc-btime}
        \caption{Local Channel Saturation Time}
        \label{fig:synwkld-local-channel-stime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/tl-btime}
        \caption{Terminal Link Saturation Time}
        \label{fig:synwkld-terminal-link-stime}
    \end{subfigure}%
   \caption{Aggregate traffic and saturation time for Workload~\Rmnum{2} under the configurations listed in Table~\ref{tab: placement routing configs}. For either contiguous or random placement, ``adp'' and ``padp'' have equivalent behavior.}
   \label{fig:synwkld-network-traffic-stime}
\end{figure*}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MultiGrid Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CrystalRouter Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MultiGrid Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CrystalRouter Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}
    \caption{Aggregate workload traffic for routers serving specific applications. More routers are involved in serving each application when random placement is in use, compared to contiguous placement. For either contiguous or random placement, ``adp'' and ``padp'' have equivalent behavior.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}
